Price of Anarchy for Mean Field Games

### 2018-07-23 PoA.tex
update prop 4 to be continue

	When $b_2 \to \infty$, we have 
	\begin{equation*}
	\begin{array}{l}
	\lambda^{b_2} \to \frac{r + \bar{r}(1-\bar{s})^2}{r + \bar{r}(1-\bar{s})} =: \lambda^{b_2 \to \infty}\\
	B^{b_2} \to \infty, \qquad B^{\eta,b_2} \to \infty\\
	C^{u,b_2} \to \lambda^{b_2 \to \infty} ( q + \bar{q}(1-s)) =: C^{u,b_2 \to \infty}, \qquad D^{u,b_2} \to \lambda^{b_2 \to \infty} (q_T + \bar{q}_T(1-s_T)) =: D^{u,b_2 \to \infty} \\
	A^{u}, A^{w}, C^w, D^w, A^{\eta}, C^{\eta}, D^{\eta} \text{ are independent of } b_2
	\end{array}
	\end{equation*}
	Moreover
	\begin{IEEEeqnarray*}{rCl}
		\frac{\delta_u^{\pm,b_2}}{b_2 + \bar{b}_2} &=& \frac{A^u}{b_2 + \bar{b}_2} \pm \sqrt{\frac{C^{u,b_2}}{r + \bar{r}(1-\bar{s})^2} + \frac{(A^u)^2}{(b_2+\bar{b}_2)^2} }\\
		&\xrightarrow[b_2 \to \infty]{}& \displaystyle \pm \sqrt{\frac{q + \bar{q}(1-s)}{r + \bar{r}(1-\bar{s})} } =: \pm c_{\delta_u^{b_2 \to \infty}}
	\end{IEEEeqnarray*}
	Thus we have $\delta^{+,b_2}_u - \delta^{-,b_2}_u \xrightarrow[b_2 \to \infty]{} +\infty$ and for any $t \in [0,T)$,
	$$\displaystyle  e^{- (\delta^{+,b_2}_u - \delta^{-,b_2}_u)(T-t)} \xrightarrow[b_2 \to \infty]{} 0.$$
	From the explicit formula (\ref{eq:riccati_ut_sol}) of $u_t^{b_2}$, we can compute the limit of $(b_2 + \bar{b}_2) u_t^{b_2}$ for any $t \in [0,T)$ by dividing the numerator with $(b_2 + \bar{b}_2)$ and the denominator with $(b_2)+\bar{b}_2)^2$, namely
	\begin{IEEEeqnarray*}{rCl}
		(b_2 + \bar{b}_2) u^{b_2}_t &=& \frac{ \displaystyle  \left(\frac{C^{u,b_2}}{b_2 + \bar{b}_2} + D^{u,b_2} \cdot \frac{\delta^{+,b_2}_u}{b_2 + \bar{b}_2}\right) - \left(\frac{C^{u,b_2}}{b_2 + \bar{b}_2} + D^{u,b_2} \cdot \frac{\delta^{-,b_2}_u}{b_2 + \bar{b}_2}\right)e^{- (\delta^{+,b_2}_u - \delta^{-,b_2}_u)(T-t)} }
		{\displaystyle \left(\frac{- \delta^{-,b_2}_u}{(b_2 + \bar{b}_2)^2} + \frac{D^{u,b_2}}{r + \bar{r}(1-\bar{s})^2} \right) + \left(\frac{\delta^{+,b_2}_u}{(b_2 + \bar{b}_2)^2} - \frac{D^{u,b_2} }{r + \bar{r}(1-\bar{s})^2} \right)e^{- (\delta^{+,b_2}_u - \delta^{-,b_2}_u)(T-t)}  } \nonumber \\
		&&\\
		&\xrightarrow[b_2 \to \infty]{}& \quad (r + \bar{r}(1-\bar{s})^2) \cdot c_{\delta_u^{b_2 \to \infty}}  =: c_3
	\end{IEEEeqnarray*}
	Idem, we can have for any $t \in [0,T)$,
	$$ (b_2 + \bar{b}_2) w_t^{b_2} \xrightarrow[b_2 \to \infty]{}  (r + \bar{r}(1-\bar{s})^2) \cdot c_{\delta_w^{b_2 \to \infty}} =: c_4,\qquad \text{with } \quad c_{\delta_w^{b_2 \to \infty}} = \sqrt{ \frac{q + \bar{q}(1-s)^2}{r + \bar{r}(1-\bar{s})^2} };$$
	and for any $t \in [0,T)$,
	$$ b_2 \eta_t^{b_2} \xrightarrow[b_2 \to \infty]{} (r+ \bar{r}) c_{\delta_\eta^{b_2 \to \infty}} =: c_5, \qquad \text{with } \quad c_{\delta_\eta^{b_2 \to \infty}} = \sqrt{\frac{q+\bar{q}}{r + \bar{r}}}.
	$$

>>>>

	When $b_2 \to \infty$, we have 
	\begin{equation*}
	\begin{array}{l}
	\lambda^{b_2} \to \frac{r + \bar{r}(1-\bar{s})^2}{r + \bar{r}(1-\bar{s})} =: \lambda^{b_2 \to \infty}\\
	B^{b_2} \to \infty, \qquad B^{\eta,b_2} \to \infty\\
	C^{u,b_2} \to \lambda^{b_2 \to \infty} ( q + \bar{q}(1-s)) =: C^{u,b_2 \to \infty}, \qquad D^{u,b_2} \to \lambda^{b_2 \to \infty} (q_T + \bar{q}_T(1-s_T)) =: D^{u,b_2 \to \infty} \\
	A^{u}, A^{w}, C^w, D^w, A^{\eta}, C^{\eta}, D^{\eta} \text{ are independent of } b_2
	\end{array}
	\end{equation*}
	Moreover
	\begin{IEEEeqnarray*}{rCl}
		\frac{\delta_u^{\pm,b_2}}{b_2 + \bar{b}_2} &=& \frac{A^u}{b_2 + \bar{b}_2} \pm \sqrt{\frac{C^{u,b_2}}{r + \bar{r}(1-\bar{s})^2} + \frac{(A^u)^2}{(b_2+\bar{b}_2)^2} }\\
		&\xrightarrow[b_2 \to \infty]{}& \displaystyle \pm \sqrt{\frac{q + \bar{q}(1-s)}{r + \bar{r}(1-\bar{s})} } =: \pm c_{\delta_u^{b_2 \to \infty}}
	\end{IEEEeqnarray*}
	Thus we have $\delta^{+,b_2}_u - \delta^{-,b_2}_u \xrightarrow[b_2 \to \infty]{} +\infty$ and for any $t \in [0,T)$,
	$$\displaystyle  e^{- (\delta^{+,b_2}_u - \delta^{-,b_2}_u)(T-t)} \xrightarrow[b_2 \to \infty]{} 0.$$
	From the explicit formula (\ref{eq:riccati_ut_sol}) of $u_t^{b_2}$, we can compute the limit of $(b_2 + \bar{b}_2) u_t^{b_2}$ for any $t \in [0,T)$ by dividing the numerator with $(b_2 + \bar{b}_2)$ and the denominator with $(b_2)+\bar{b}_2)^2$, namely
	\begin{IEEEeqnarray*}{rCl}
		(b_2 + \bar{b}_2) u^{b_2}_t &=& \frac{ \displaystyle  \left(\frac{C^{u,b_2}}{b_2 + \bar{b}_2} + D^{u,b_2} \cdot \frac{\delta^{+,b_2}_u}{b_2 + \bar{b}_2}\right) - \left(\frac{C^{u,b_2}}{b_2 + \bar{b}_2} + D^{u,b_2} \cdot \frac{\delta^{-,b_2}_u}{b_2 + \bar{b}_2}\right)e^{- (\delta^{+,b_2}_u - \delta^{-,b_2}_u)(T-t)} }
		{\displaystyle \left(\frac{- \delta^{-,b_2}_u}{(b_2 + \bar{b}_2)^2} + \frac{D^{u,b_2}}{r + \bar{r}(1-\bar{s})^2} \right) + \left(\frac{\delta^{+,b_2}_u}{(b_2 + \bar{b}_2)^2} - \frac{D^{u,b_2} }{r + \bar{r}(1-\bar{s})^2} \right)e^{- (\delta^{+,b_2}_u - \delta^{-,b_2}_u)(T-t)}  } \nonumber \\
		&&\\
		&\xrightarrow[b_2 \to \infty]{}& \quad (r + \bar{r}(1-\bar{s})^2) \cdot c_{\delta_u^{b_2 \to \infty}}  =: c_u
	\end{IEEEeqnarray*}
	Idem, we can have for any $t \in [0,T)$,
	$$ (b_2 + \bar{b}_2) w_t^{b_2} \xrightarrow[b_2 \to \infty]{}  (r + \bar{r}(1-\bar{s})^2) \cdot c_{\delta_w^{b_2 \to \infty}} =: c_w,\qquad \text{with } \quad c_{\delta_w^{b_2 \to \infty}} = \sqrt{ \frac{q + \bar{q}(1-s)^2}{r + \bar{r}(1-\bar{s})^2} }.$$
%	and for any $t \in [0,T)$,
%	$$ b_2 \eta_t^{b_2} \xrightarrow[b_2 \to \infty]{} (r+ \bar{r}) c_{\delta_\eta^{b_2 \to \infty}} =: c_5, \qquad \text{with } \quad c_{\delta_\eta^{b_2 \to \infty}} = \sqrt{\frac{q+\bar{q}}{r + \bar{r}}}.
%	$$

	Moreover, we can derive a uniform lower bound for $(b_2 + \bar{b}_2) u_t^{b_2}$ for any large enough $b_2$ by expanding this whole expression with equation (\ref{eq:riccati_ut_sol}). Let $\epsilon_1 > 0$ so that $\epsilon_1 < \min \{ c_{\delta_u^{b_2 \to \infty}}, D^{u,b_2 \to \infty} \}$. Then there exists $b_2^{*,lower}>0$ such that for all $b_2 \geq b_2^{*,lower}$ we have:
	$$ 
	\max \left\{  \left\vert \frac{\delta_u^{+,b_2}}{b_2 + \bar{b}_2}  - c_{\delta_u^{b_2 \to \infty}} \right\vert, \   \left\vert \frac{\delta_u^{-,b_2}}{b_2 + \bar{b}_2}  - (-c_{\delta_u^{b_2 \to \infty}}) \right\vert, \vert D^{u,b_2} - D^{u,b_2\to \infty} \vert  \right\} \leq \epsilon_1,
	$$ 
	so that
	\begin{IEEEeqnarray}{rCl}
		(b_2 + \bar{b}_2) u_t^{b_2} &\geq&  (b_2 + \bar{b}_2) \frac{D^{u,b_2} \delta_u^{+, b_2} }{ (\delta_u^{+,b_2} - \delta_u^{-,b_2}) + B^{b_2}D^{u,b_2} } \nonumber \\
		&=& \frac{D^{u,b_2} \frac{\delta_u^{+, b_2}}{b_2+ \bar{b}_2} }{ \frac{\delta_u^{+,b_2} - \delta_u^{-,b_2}}{b_2 + \bar{b}_2} + \frac{D^{u,b_2}}{r + \bar{r}(1-\bar{s})^2} } \nonumber \\
		&\geq& \frac{(D^{u,b_2 \to \infty} - \epsilon_1 ) \cdot (c_{\delta_u^{b_2 \to \infty}} - \epsilon_1) }{ (2 c_{\delta_u^{b_2 \to \infty}} + 2 \epsilon_1) + (D^{u,b_2 \to \infty} + \epsilon_1) / (r+ \bar{r}(1-\bar{s})^2) } =: m_u(\epsilon_1)
	\end{IEEEeqnarray}

	% upper bound for u_t, w_t
	Also, from the explicit formula (\ref{eq:riccati_ut_sol}) of $u_t^{b_2}$, given any fixed $b_2$, we can compute the derivative of $u_t^{b_2}$ with respect to time $t$ and obtain:
	\begin{equation}
		\frac{d u_t^{b_2}}{dt} = \frac{\left(B^{b_2} (D^{u,b_2})^2 + 2 A^u D^{u,b_2} - C^{u,b_2} \right) \cdot (\delta_u^{+,b_2} - \delta_u^{-,b_2}) e^{- (\delta_u^{+,b_2} - \delta_u^{-,b_2})(T-t) } }{\left[(- \delta_u^{-,b_2} + B^{b_2} D^{u,b_2} )  + (\delta_u^{+,b_2} - B^{b_2} D^{u,b_2} )e^{- (\delta_u^{+,b_2} - \delta_u^{-,b_2})(T-t)} \right]^2 }
	\end{equation}
	Hence $t \mapsto u_t^{b_2}$ is increasing when $B^{b_2} (D^{u,b_2})^2 + 2 A^u D^{u,b_2} - C^{u,b_2} > 0$. Since 
	$$ B^{b_2} (D^{u,b_2})^2 + 2 A^u D^{u,b_2} - C^{u,b_2} \xrightarrow[b_2 \to \infty]{} \infty,$$
	there must exists $b_2^{*,u,upper}>0$ such that for all $b_2 \geq b_2^{*,u,upper}$ we have $t \mapsto u_t^{b_2}$ being an increasing function and 
	$$ \sup_{b_2 \geq b_2^{*,u,upper}} \sup_{0\leq t \leq T} \left\{ u_t^{b_2} \right\} \leq \sup_{b_2 \geq b_2^{*,u,upper}} \left\{ u_T^{b_2}\right\}  = \sup_{b_2 \geq b_2^{*,u,upper}} \{ D^{u,b_2}  \} \leq D^{u,b_2 \to \infty} + 1.$$
	Idem for $t \mapsto w_t^{b_2}$. Let $b_2^{*,upper} = \max \{ b_2^{*,u,upper}, b_2^{*,w,upper}\}$ and $M = \max \{  D^{u,b_2 \to \infty}+1, D^w+1\}$, we have a uniform upper bound for $u_t^{b_2}$ and $w_t^{b_2}$ for all $b_2$ large enough,namely
	\begin{equation}
	\sup_{b_2 \geq b_2^{*,upper}} \sup_{0 \leq t \leq T} \max \left\{ u_t^{b_2} , w_t^{b_2}\right\} \leq M.
	\label{eq:ut_wt_upper_bound_b2_infty}
	\end{equation}
